elton trait

### 2019-07-02 data-raw/elton.Rmd
Include all trait data, even species without id's. Standardize origin sci name column name.

#join on scientific and common
sci_matches <- bird_ids  %>%
  filter(match_type == "scientific") %>%
  select(id = acceptedNameUsageID, input, scientificName) %>%
  distinct() %>%
  right_join(bird_trait %>% select(.dots = -col_ex), by = c("input" = "scientific"), na_matches = "never") %>%
  drop_na(id) %>%
  distinct() %>%
  select(-english)

@@

#there are more rows after ID data is joined because for species that matched on common names there may be more than one scientificName 
elton_bird <- bind_rows(sci_matches, comm_matches)
```

Do the same for mammal trait data
```{r}
elton_mamm <- mammal_ids %>%
  select(id = acceptedNameUsageID, input, scientificName) %>%
  right_join(mamm_trait %>% select(-mswfamilylatin), by = c("input" = "scientific"), na_matches = "never") %>%
  drop_na(id) %>%
  distinct() 
```

>>>>

#join on scientific and common
sci_matches <- bird_ids  %>%
  filter(match_type == "scientific") %>%
  select(id = acceptedNameUsageID, input, scientificName) %>%
  distinct() %>%
  right_join(bird_trait %>% select(.dots = -col_ex), by = c("input" = "scientific"), na_matches = "never") %>%
  #drop_na(id) %>%
  distinct() %>%
  select(-english)

@@

#there are more rows after ID data is joined because for species that matched on common names there may be more than one scientificName 
elton_bird <- bind_rows(sci_matches, comm_matches) %>% rename(sourceName = input)
```

Do the same for mammal trait data
```{r}
elton_mamm <- mammal_ids %>%
  select(id = acceptedNameUsageID, input, scientificName) %>%
  right_join(mamm_trait %>% select(-mswfamilylatin), by = c("input" = "scientific"), na_matches = "never") %>%
  distinct() %>%
  rename(sourceName = input)
```
